Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Add paper on bug tracking systems

>>>>

\textbf{Towards the Next Generation of Bug Tracking Systems}\cite{just2008towards}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The authors wanted to determine what makes for good bug reports and, more specifically, how the reporting environment can be changed to best suit the developers’ needs (and everyone else involved in the software project). 
  \item \textbf{What was the method?}
  They first launched a survey to developers from Eclipse, Mozilla and Apache open source projects from which they received 175 comments back. Then, they applied a card sort in order to organize the comments into hierarchies to deduce a higher level of abstraction and identify common patterns. 
  \item \textbf{What did they learn?}
  They found 7 main topics of improvement for bug tracking systems: provide tool support for users to collect and prepare information that developers need, find volunteers to translate bug reports filed in foreign languages, provide different user interfaces for each user level and give cues to inexperienced reporters on what to report and best practices, reward reporters when they do a good job, integrate reputation into user profiles to mark experienced reporters, provide powerful and easy to use tools to search bug reports, encourage users to submit additional details (provide tools for merging bugs). 
  \item \textbf{Relevance to our work}:
  This is an important paper to our research as it presents, from open source developers’ perspective, how bug reporting and bug tracking systems should behave. This research gives us various topics to concentrate on when analyzing the quality of tickets. 
\end{itemize}
